TODO: A Survey of StarCraft AI Techniques

### 2012-07-19 survey.tex
competition results of CIG 2011 completed

At CIG 2011, the tournament was therefore run with a (secret) selection
of maps used in league play. It was organized by Tobias Mahlmann and Mike
Preuss and attracted 10 bots. In addition to the ones discussed in previous
sections (UAlbertaBot, Skynet, AIUR, Nova, BroodwarBotQ, BTHAI), 
the set also contained LSAI, Xelnaga, Protoss Beast Jelly, and EvoBot,
these are shortly described in the following:

@@

\begin{table*}[htb]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:correlations}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket A} \\ \hline
Crashes & games & bot	& wins\\ \hline
0 &	 40 &	 UAlbertaBot &	 33\\
1 &   40 &	 Skynet	  &  31\\
2 &	 40 &	 AIUR	  &  24\\
1 &	 40 &	 Nova	  &  8\\
0 &	 40 &	 LSAI	  &  4\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket B} \\ \hline
Crashes & games & bot	& wins\\ \hline
12 &	 40 &	 Xelnaga &	 25\\
3 &   40 &	 BroodwarBotQ  &  23 (6)\\
0 &	 40 &	 BTHAI	  &  23 (4)\\
17 &	 40 &	 Protoss Beast Jelly  & 17\\
0 &	 40 &	 EvoBot	  &  12\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

As BroodwarBotQ and BTHAI have the same number of wins, their direct encounter is evaluated which accounted 6 : 4 for the BroodwarBotQ.
Note that all qualified bots play Protoss.

Maps used for the first round: (2)MatchPoint 1.3, (4)Fighting Spirit 1.3, iCCupdestination 1.1, iCCup gaia, iCCup great barrier reef

Final Round

The final round was played in a similar mode as each of the first round brackets, using another set of 5 maps (see below), resulting in 30 games for each bot.

Crashes	 Games	 Bot	 Wins
0	 30	 Skynet	 26
0	 30	 UAlbertaBot	 22
3	 30	 Xelnaga	 11
2	 30	 BroodwarBotQ	 1

Here describe the results obtained in the competition comparing the bots.
}

>>>>

At CIG 2011, the tournament was therefore run with a (secret) selection
of maps used in league play, which can be regarded as the most important
difference to the AIIDE tournament that employed a known list of maps.
The competition was organized by Tobias Mahlmann and Mike
Preuss and attracted 10 bots. In addition to the ones discussed in previous
sections (UAlbertaBot, Skynet, AIUR, Nova, BroodwarBotQ, BTHAI), 
the set also contained LSAI, Xelnaga, Protoss Beast Jelly, and EvoBot,
these are shortly described in the following:

@@

\begin{table*}[htb]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:cig-first-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket A} \\ \hline
Crashes & games & bot	& wins\\ \hline
0 &	 40 &	 UAlbertaBot &	 33\\
1 &   40 &	 Skynet	  &  31\\
2 &	 40 &	 AIUR	  &  24\\
1 &	 40 &	 Nova	  &  8\\
0 &	 40 &	 LSAI	  &  4\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket B} \\ \hline
Crashes & games & bot	& wins\\ \hline
12 &	 40 &	 Xelnaga &	 25\\
3 &   40 &	 BroodwarBotQ  &  23 (6)\\
0 &	 40 &	 BTHAI	  &  23 (4)\\
17 &	 40 &	 Protoss Beast Jelly  & 17\\
0 &	 40 &	 EvoBot	  &  12\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

\subsubsection{First Round}
\label{sec:cig-first-round}

As the CIG competition games were executed manually due to
a lack of available software (the AIIDE program was not yet
available at that time), we separated the ten entries into
two brackets. In each bracket of 5 bots, a round-robin
tournament was held with 10 repetitions per pairing, resulting
in 40 games per bot.
The 5 maps chosen for the first round were selected from the pool
of well-known league play maps found on the internet:
\emph{(2)MatchPoint 1.3}, \emph{(4)Fighting Spirit 1.3}, 
\emph{iCCupdestination 1.1}, \emph{iCCup gaia}, and 
\emph{iCCup great barrier reef}. Each bot pairing played
on every map twice, with switched starting positions.

The two top bots of every bracket qualified
for the final round. Table~\ref{tab:cig-first-round} summarizes
the results.
Note that as BroodwarBotQ and BTHAI have the same number of wins,
their direct encounter was evaluated which accounted 6:4 for the BroodwarBotQ.
The bots going into the final were thus UAlbertaBot, Skynet (from bracket A)
and Xelnaga and BroodwarBotQ (from bracket B). All qualified bots play the
Protoss faction. Most bots proved pretty stable, only Xelnaga and Protoss 
Beast Jelly crashed relatively often (each in more than a quarter of the games). 
Crashing of course resulted in an instant win for the other bot.
In some cases, neither bot was able to finish the other off completely,
so that they went into a passive state. We manually ended such games after
around 15 minutes and assigned victory to the bot that had obtained more
points as indicated on the end game screen.

\subsubsection{Final Round}
\label{sec:cig-final-round}

The final round was played in a similar mode as each of the
first round brackets,
using another set of 5 previously unknown maps:
\emph{iCCup lost temple 2.4}, \emph{iCCup rush hour 3.1},
\emph{iCCup swordinthemoon 2.1}, \emph{iCCup yellow 1.1},
and \emph{La\_Mancha 1.1}. 
Letting each pairing play on each map twice again with
switching starting positions resulted in 30 games per bot.
The final results are displayed in table~\ref{tab:cig-final-round},
indicating Skynet as winner and UAlbertaBot as runner-up, being
almost equally strong, and the two other bots as clearly inferior.

\begin{table}[bth]
\caption{Results of the CIG 2011 final round.}
\label{tab:cig-final-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|}
\hline
Crashes & games & bot	& wins\\ \hline
0 &  30 &	 Skynet	  		&  26\\
0 &	 30 &	 UAlbertaBot 	&  22\\
3 &	 30 &	 Xelnaga  		&  11\\
2 &	 30 &	 BroodwarBotQ  	&  1\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table}

}
